PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$

### 2014-10-20 qfenv_paper/qf_environment.tex
multipanel qf fit literature comparison figures

\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_zcosmoscomp_envthresh_kovacoffset.eps, height=0.45\textwidth}
        \caption{$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\rm{red}}(\mathcal{M}_{*}=10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Iovino:2010aa} (square) and \cite{Kovac:2014aa} (triangle) from zCOSMOS and \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross) from SDSS. The $f_{\rm{red}}$ values from \cite{Iovino:2010aa}, \cite{Kovac:2014aa}, and \cite{Baldry:2006aa} are calculated from the best-fit parameterizations presented in the respective works. The $f_{\rm{Q}}$ value from \cite{geha12a} is the $f_{\rm{Q}}$ value at $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$. High density environment is represented in red and low density environment is represented in blue. For \cite{Kovac:2014aa} we apply the offset between the color-based and SFR-based galaxy classification in order to plot the $f_{\rm{Q}}$ estimates. We also plot the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution of our sample with varying environment cut-offs specified on the top right. As in Figure \ref{fig:qffit} the width of the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution represent the uncertainty in the best-fit parameters of Equation \ref{eq:qffit}.}         \label{fig:qffit_comp}
    \end{center}
\end{figure}

>>>>

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_baldry_geha_iovino_kovac_peng_envthresh_kovacoffset.eps, height=\textwidth, angle=90}
        \caption{$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\rm{red}}(\mathcal{M}_{*}=10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross) from SDSS (panel a), \cite{Iovino:2010aa} (empty square) and \cite{Kovac:2014aa} (triangle) from zCOSMOS (panel b), and \cite{Peng:2010aa} (filled square) from SDSS and zCOSMOS (panel c). The $f_{\rm{red}}$ values from \cite{Iovino:2010aa}, \cite{Kovac:2014aa}, \cite{Baldry:2006aa}, and \cite{Peng:2010aa} are calculated from the best-fit parameterizations presented in the respective works. The $f_{\rm{Q}}$ value from \cite{geha12a} is the $f_{\rm{Q}}$ value at $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$. High density environment is represented in red and low density environment is represented in blue. For \cite{Kovac:2014aa} we apply the offset between the color-based and SFR-based galaxy classification in order to plot the $f_{\rm{Q}}$ estimates. We also plot the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution of our sample with varying environment cut-offs specified on the top right. As in Figure \ref{fig:qffit} the width of the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution represent the uncertainty in the best-fit parameters of Equation \ref{eq:qffit}.}         \label{fig:qffit_comp}
    \end{center}
\end{figure*}
